### 2015-02-12 fundamentals/intro.tex
adds erich definition of fcs

Historically, nuclear fuel cycle simulators have calculated
fuel cycle mass balances and performance metrics derived from them using software
ranging from ad hoc spreadsheet-driven flow calculators to highly specialized
system dynamics modeling platforms. To date, current tools are either static, fleet-based,
privately distributed, or all of the above. Each of these qualities presents a
challenge to modeling fidelity, generality, efficiency, robustness, and
scientific transparency.

>>>>

The cardinal purpose of a nuclear fuel cycle simulator is to calculate the
time- and facility-dependent mass flow through all or part the fuel cycle. Many
architecture choices are discussed in \ref{sec:litrev}.  Historically, nuclear
fuel cycle simulators have calculated fuel cycle mass balances and performance
metrics derived from them using software ranging from ad hoc spreadsheet-driven
flow calculators to highly specialized system dynamics modeling platforms. To
date, current tools are often static rather than dynamic, rigid rather than
flexible, fleet-based rather than discrete, or privately distributed rather
than open source. Each of these choices presents a challenge to modeling
fidelity, generality, efficiency, robustness, and scientific transparency.
